curiobaby_drop model analysis

### 2021-01-31 analysis/model_analysis_v2.Rmd

```{r, load-data}
raw <- read.table(here("models/model_stats.csv"), sep=',')
cnames <- raw[1,]
mdat <- raw[2:nrow(raw),]
names(mdat) = cnames
for(c in 1:(ncol(mdat)-3)) {
  mdat[,c] = as.numeric(mdat[,c])
}
mdat$trial = rep(1:20, each=2)
# right now, each trial is 2 rows, 
# uniquely identified with drop_object x condition
#mdat %>% distinct(drop_object, condition)

mdat <- mdat %>% rename(drop = drop_object,
                        target = target_object,
                        relation = condition) %>%
  mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism"))

@@

# engineer some features: 
# combine target + drop target features
mdat_eng <- mdat %>%
  mutate(obj_final_position_std = 
           `obj_final_position_std_objects=drop` + 
           `obj_final_position_std_objects=target`,
         normed_velocity_std_after_first_collision_objects = 
           `normed_velocity_std_after_first_collision_objects=drop` + 
           `normed_velocity_std_after_first_collision_objects=target`,
         avg_final_radius_objects = 
           `avg_final_radius_objects=drop` + 
           `avg_final_radius_objects=target`,
         avg_max_radius_objects = 
           `avg_max_radius_objects=drop` + 
           `avg_max_radius_objects=target`,
         max_radius_std_objects = 
           `max_radius_std_objects=drop` + 
           `max_radius_std_objects=target`,
         support_combo = 
           support_probability + 
           support_std + 
           `support_response_sharpness_C=1e-05`, # add one of support_response_linearity_r or _pv ?
         len_combo = avg_len + len_std + len_inverse_sharpe_ratio
         ) %>%
  select(-`obj_final_position_std_objects=drop`, 
         -`obj_final_position_std_objects=target`,
         -`normed_velocity_std_after_first_collision_objects=drop`,
         -`normed_velocity_std_after_first_collision_objects=target`,
         -`avg_final_radius_objects=drop`,
         -`avg_final_radius_objects=target`,
         -`avg_max_radius_objects=drop`,
         -`avg_max_radius_objects=target`,
         -`max_radius_std_objects=drop`,
         -`max_radius_std_objects=target`,
         -support_probability, 
         -support_std,
         -`support_response_sharpness_C=1`,
         -`support_response_sharpness_C=1e-05`,
         -`support_response_sharpness_C=100000.0`,
         -avg_len, -len_inverse_sharpe_ratio, -len_std,
         -support_response_linearity_pv, -support_response_linearity_r,
         -`obj_final_position_invstd_objects=target`,
         -`obj_final_position_invstd_objects=drop`
         )

@@

softmax <- function(weights, beta=1, smooth=1e-7) {
  weights = weights + smooth
  probs = (weights / sum(weights)) # normalize first
  num <- exp(beta * probs)
  return(num / sum(num))
}

@@

adult_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                feat_df=feat_df, hum_df=adult_trial_agg)
}
```

# Compare to children's choices

```{r}
child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

child_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
```

@@

```{r adult-eng-feats}
feat_names2 = names(mdat_eng)[5:ncol(mdat_eng)]

for(feat in feat_names2) {
  feat_df <- get_feature_df(mdat_eng, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                feat_df=feat_df, hum_df=adult_trial_agg)
  child_fits[[feat]] = DEoptim(evalFit, lower=.7, upper=5, DEoptim.control(reltol=.001, NP=30, itermax=70), 
                feat_df=feat_df, hum_df=child_trial_agg)
}

>>>>

```{r, load-data}

@@

load_data <- function(fname) {
  raw <- read.table(here(paste0("models/",fname,".csv")), sep=',')
  cnames <- raw[1,]
  mdat <- raw[2:nrow(raw),]
  names(mdat) = cnames
  for(c in 1:(ncol(mdat)-3)) {
    mdat[,c] = as.numeric(mdat[,c])
    if(min(mdat[,c]) < 0) mdat[,c] = mdat[,c] + min(mdat[,c])
    print(paste("shifting",c,"so minimum is 0"))
  }
  mdat$trial = rep(1:20, each=2)
  # right now, each trial is 2 rows, 
  # uniquely identified with drop_object x condition
  #mdat %>% distinct(drop_object, condition)

  mdat <- mdat %>% rename(drop = drop_object,
                          target = target_object,
                          relation = condition) %>%
    mutate(drop = replace(drop, drop=="triangular_prism", "trig prism"),
         target = replace(target, target=="triangular_prism", "trig prism"))
  return(mdat)
}

# just 100 drops per trial
mdat100 <- load_data("model_stats")

mdat <- load_data("model_stats250")

sort(colMeans(mdat[,1:43]))
# mean of obj_final_position_invstd_objects=drop is negative..
# mean of avg_len is 235, and len_std is 45 (much larger than typical feature mean on order of .1 - 1.0)
# scale these cols? (only matters for their combination)
mdat$avg_len = mdat$avg_len / max(mdat$avg_len)
mdat$len_std = mdat$len_std / max(mdat$len_std)

# engineer some features: 
# combine target + drop target features
mdat_eng <- mdat %>%
  rowwise() %>%
  mutate(obj_final_position_std = mean(`obj_final_position_std_objects=drop`,
                                       `obj_final_position_std_objects=target`),
         normed_velocity_std_after_first_collision_objects = 
           mean(`normed_velocity_std_after_first_collision_objects=drop`,
                `normed_velocity_std_after_first_collision_objects=target`),
         avg_final_radius_objects = mean(`avg_final_radius_objects=drop`, 
                                         `avg_final_radius_objects=target`),
         avg_max_radius_objects = mean(`avg_max_radius_objects=drop`,
                                       `avg_max_radius_objects=target`),
         max_radius_std_objects = mean(`max_radius_std_objects=drop`,
                                       `max_radius_std_objects=target`),
         support_combo = mean(support_probability, support_std, 
                              `support_response_sharpness_C=1`, # add support_response_linearity_r or _pv ?
                              `support_response_sharpness_accuracy_C=1`),
         support_sharpness_mean = mean(`support_response_sharpness_C=1e-05`,
                                       `support_response_sharpness_C=0.0001`,
                                       `support_response_sharpness_C=0.001`,
                                       `support_response_sharpness_C=0.01`,
                                       `support_response_sharpness_C=0.1`,
                                       `support_response_sharpness_C=1`,
                                       `support_response_sharpness_C=10.0`,
                                       `support_response_sharpness_C=100.0`,
                                       `support_response_sharpness_C=1000.0`,
                                       `support_response_sharpness_C=10000.0`,
                                       `support_response_sharpness_C=100000.0`),
         support_sharpness_accuracy_mean = mean(
            `support_response_sharpness_accuracy_C=1e-05`,
             `support_response_sharpness_accuracy_C=0.0001`,
             `support_response_sharpness_accuracy_C=0.001`,
             `support_response_sharpness_accuracy_C=0.01`,
             `support_response_sharpness_accuracy_C=0.1`,
             `support_response_sharpness_accuracy_C=1`,
             `support_response_sharpness_accuracy_C=10.0`,
             `support_response_sharpness_accuracy_C=100.0`,
             `support_response_sharpness_accuracy_C=1000.0`,
             `support_response_sharpness_accuracy_C=10000.0`,
             `support_response_sharpness_accuracy_C=100000.0`),
         support_response_linearity_mean = mean(support_response_linearity_pv, 
                                                support_response_linearity_r),
         len_combo = mean(avg_len, len_std, len_inverse_sharpe_ratio)
         ) %>%
  select(obj_final_position_std, 
         normed_velocity_std_after_first_collision_objects, 
         avg_final_radius_objects,
         avg_max_radius_objects,
         max_radius_std_objects,
         support_combo, 
         support_sharpness_mean,
         support_sharpness_accuracy_mean,
         len_combo,
         drop, target, relation)

@@

softmax <- function(weights, beta=1, smooth=1e-7) {
  weights = weights + smooth
  probs = (weights / sum(weights)) # normalize first
  num <- exp(beta * probs)
  return(num / sum(num))
}
# softmax(c(.7,.3), beta=2)

@@

child_trial_agg <- child_long %>% group_by(relation, drop, target) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T), n=n())

adult_fits = list()
child_fits = list()
for(feat in feat_names) {
  feat_df <- get_feature_df(mdat, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                feat_df=feat_df, hum_df=adult_trial_agg)
  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
```

@@

```{r adult-eng-feats}
feat_names2 = names(mdat_eng)[1:(ncol(mdat_eng)-3)]

for(feat in feat_names2) {
  feat_df <- get_feature_df(mdat_eng, feat)
  #paste(feat, evalFit(feat_df, adult_trial_agg, 1))
  adult_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                feat_df=feat_df, hum_df=adult_trial_agg)
  child_fits[[feat]] = DEoptim(evalFit, lower=.5, upper=10, DEoptim.control(reltol=.001, NP=30, itermax=20), 
                feat_df=feat_df, hum_df=child_trial_agg)
}
